%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, letterpaper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[rectangle,edge,right]{./examples/profile}
\name{Ruud}{Voorjans}
\position{Software / DevOps Engineer}
\address{Simpelveld}


\email{ruud.voorjans@parkhost.eu}

\github{parkhost}

\linkedin{parkhost}


% \quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[C]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Ruud Voorjans~~~·~~~Resume}
  {\thepage}

\cvsection{Summary}
\begin{cvparagraph}

More than 10 years of sysadmin experience in different environments and operating systems. Experience in maintaining (micro)services in Kubernetes and Docker with methods/principals as IaC, CI/CD, GitOps. Developing (automation) software in scrum/agile way. 

\end{cvparagraph}

\cvsection{Work Experience}
\begin{cventries}


  \cventry
    {DevOps/Software engineer}
    {KEMBIT}
    {Wijnandsrade}
    {Jan 2022 - Present}
    {
      \begin{cvitems}
        \item{Managing services in Docker containers and Kubernetes Clusters.}
        \item{Automating IT tasks as an MSP (customer independant).}
        \item{Synchronizing data between information systems.}
        \item{Creating and connecting the "dots"}
      \end{cvitems}
    }


  \cventry
    {System Administrator}
    {KEMBIT}
    {Wijnandsrade}
    {Aug 2018 - Dec 2021}
    {
      \begin{cvitems}
        \item{Maintained IT (server) environments; onpremise and cloud (Azure).}
        \item{Investigate and solving problems within different (customer) environments.}
        \item{Created technical design; Continuous application integration/deployment with C4B.}
        \item{Applying (complex) changes.}
        \item{Purpose several improvements to give the customer a better experience}
      \end{cvitems}
    }


  \cventry
    {Servicedesk / System Administrator}
    {TRUE}
    {Beek (MAA)}
    {Aug 2017 - Jul 2018}
    {
      \begin{cvitems}
        \item{Managed onpremise Microsoft environment}
        \item{Maintained Debian and FreeBSD web hosting environments}
        \item{Managed Networking/Firewall (Juniper / PfSense / Fortinet)}
      \end{cvitems}
    }


  \cventry
    {System/Network Administrator}
    {MeanderGroep}
    {Landgraaf}
    {Jul 2015 - Aug 2017}
    {
      \begin{cvitems}
        \item{System Administrator (Microsoft)}
        \item{Network Engineer (Cisco)}
      \end{cvitems}
    }


  \cventry
    {Project Engineer}
    {Data4}
    {Beek (MAA)}
    {Apr 2013 - Nov 2015}
    {
      \begin{cvitems}
        \item{Several projects at different companies}
        \item{Mostly migration projects to newer Operating systems / Cloud}
        \item{Skilled Servicedesk at Maastricht University Medical Centre (MUMC)}
      \end{cvitems}
    }


  \cventry
    {Service Desk}
    {GETRONICS / KPN}
    {Beek (MAA)}
    {Aug 2010 - Mar 2013}
    {
      \begin{cvitems}
        \item{Various IT Servicedesk tasks (incidents, changes) at large national companies and government}
      \end{cvitems}
    }



\end{cventries}

\cvsection{Certifications}
\begin{cvhonors}

  \cvhonor
    {ITIL Foundation Certificate in IT Service Management}
    {Certification ID: 5.61768920506583e+06}
    {EXIN}
    {Feb 2016}

  \cvhonor
    {Cisco Certified Network Associate Routing and Switching}
    {Certification ID: 427924169524DTDF}
    {Cisco}
    {Feb 2017}

  \cvhonor
    {Information Security Foundation based on ISO IEC 27001}
    {Certification ID: 6269146}
    {EXIN}
    {May 2019}

  \cvhonor
    {MCSA Windows 10 Certified 2019}
    {Certification ID: H070-9469}
    {Microsoft}
    {Nov 2019}

  \cvhonor
    {M365 Modern Desktop Administrator Associate}
    {Certification ID: H357-2019}
    {Microsoft}
    {Feb 2020}

  \cvhonor
    {Azure Administrator Associate}
    {Certification ID: 16560902}
    {Microsoft}
    {Aug 2020}

  \cvhonor
    {Microsoft Azure Developer Associate}
    {Certification ID: 16560902}
    {Microsoft}
    {Oct 2021}


\end{cvhonors}

\cvsection{Projects}
\begin{cventries}

  \cventry
    {Creator}
    {Hosting/Creating blog / wiki(.js)}
    {wiki.parkhost.eu}
    {Markdown / Docker / Kubernetes}
    {Notes/documentation of things that interests me.}

  \cventry
    {Creator}
    {Custom CVE API}
    {cve.parkhost.eu}
    {Node.js / TypeScript / MongoDB / Docker}
    {Used Mongodb to store CVE's in json, custom indexing for rapid lookups. FeatherJS as custom RESTapi and VUE.js in front.}

  \cventry
    {Creator}
    {Maintaining -Azure Kubernetes Service- cluster}
    {wikitest.parkhost.eu}
    {Terraform / ArgoCD / Azure DevOps / k8s}
    {Maintaining my aks cluster with principals as IaC, GitOps, CI/CD and Automation.}

  \cventry
    {Creator}
    {Kubernetes and Windows}
    {https://github.com/Parkhost/KubernetesonWindows}
    {Powershell / Bash}
    {Mixed OS Windows Node on a kubeadm bootstrapt cluster with containerd as CRI and flannel as CNI.}

  \cventry
    {Creator}
    {Script for a Script}
    {github.com/ParkHost/Script-for-Script}
    {Powershell}
    {Script and a Service, to help secure windows.}


\end{cventries}

\cvsection{Education}
\begin{cventries}

  \cventry
    {MBO 4 ICT - System Administrator}
    {Arcus College}
    {Heerlen}
    {2005 - 2010}
    {
    }


\end{cventries}

%-------------------------------------------------------------------------------
\end{document}
